Referee report checklist

### 2021-01-07 Revision/list.tex
minor change to response to the AE

\response{We include another example of forecasting the stock price of Apple Inc. during MacBook release in 2020 in Section 5.2 of the revised manuscript. Our method nearly perfectly recovers its stock price of the day after the release date. The donor pool constructed includes three time series of  Apple inc.'s stock price during MacBook release in the past three years. In this example, the shock is with precedent and our method works well because Apple Inc. is a well-established company that is not expected to reform its products a lot. As a result, knowledge from past shocks can bring insights into the future shocks. This example is representative for applying our methods to the time series that are to experience a shock that is with precedent in the past. In contrast, the example of Conoco Phillips is without precedent. In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by  pandemic. In this example, our method is better than the original forecast though it cannot fully recover the stock price. \\

In summary, the Apple example and Conoco Phillips example are representative of time series that are to experience precedented and unprecedented shocks, respectively. We think they generate confidence in our proposed approach since they  represent a wide range of applications in the real life. To support, the simulation  in Section 4 also informs  users the situations when our methods will work well and will not.
}

>>>>

\response{We include another example of forecasting the stock price of Apple Inc. during MacBook release in 2020 in Section 5.2 of the revised manuscript. Our method nearly perfectly recovers its stock price of the day after the release date. The donor pool constructed includes three time series of  Apple inc.'s stock price during MacBook release in the past three years. In this example, the shock is with precedent and our method works well because Apple Inc. is a well-established company that is not expected to reform its products a lot. As a result, knowledge from past shocks can bring insights into the future shocks. This example is representative for applying our methods to the time series that are to experience a shock that is with precedent in the past. In contrast, the example of Conoco Phillips is without precedent. In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by  pandemic. In this example, our method is better than the original forecast though it cannot fully recover the stock price. We hope that the addition of the Apple example helps to generate confidence in our approach.
}
